GBM Proteomics and Proteolytic processing data analysis - Reproducible report

### 2022-01-25 scr/gbm_proteomics_data_analysis_proteolytic_products_prep_figures_v3_gh_format.Rmd
modify Rmd and md; add figures; add results

@@

@@

```{r}
plotSumEM
```

@@

@@

write_tsv(x = decreased_Rec,
          file = here("results/semi_tryptic/proteolytic_products_increased_in_Recurrent.tsv"))

>>>>

pep_quant_presummary_semi <- pep_quant_presummary %>%
  filter(specificity == "semi_specific",
         is_terminal == "not_terminal")
```

@@

# summary of sum of log2 semi-specific peptides per sample

pept_summary_semi_1 <- pep_quant_presummary_semi %>% 
  group_by(paired_id, recurrence) %>%
  summarise(Sum_All = sum(Abundance, na.rm = TRUE)) %>%
  mutate(Stage = if_else(recurrence == "prim",
                         true = "Initial",
                         false = "Recurrence"),
         `Summed Abundances` = Sum_All)

@@

@@

### Generate plot of sum of abundances semi-specific peptides

```{r}
sum_semi_abunds <- ggplot(pept_summary_semi_1, 
                    aes(x = Stage, 
                        y = `Summed Abundances`, fill = Stage, 
                        cex.axis = 1.5)) +
  geom_boxplot() +
  #geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 0.5,
  #             ) +
  geom_jitter(position=position_jitter(0.2)) + 
  # Box plot with jittered points
  # 0.2 : degree of jitter in x direction
  # geom_jitter(shape=16, position=position_jitter(0.2))
  ylab("Sum of log2-intensities of semi-tryptic peptides") +
  geom_signif(
    comparisons = list(c("Initial", "Recurrence")),
    map_signif_level = TRUE
  ) + 
  stat_compare_means(method="t.test") +
  theme(axis.text.x = element_text(hjust = 0.5, vjust = 0, size = 6, angle = 360),
        axis.text.y = element_text(hjust = 0.95, vjust = 0.2, size = 8),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=0.5),
        axis.title = element_text(size = 8),
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 8),
        legend.key.height= unit(3, 'mm'),
        legend.key.width= unit(3, 'mm'),
        legend.position="bottom")
```

```{r}
ggsave(plot = sum_semi_abunds, 
       filename = here::here("figures/box_sum_semispec_pepts.tiff"), 
       device = "tiff",
       units = "mm",
       width = 40,
       height = 50)

ggsave(plot = sum_semi_abunds, 
       filename = here::here("figures/box_sum_semispec_pepts.eps"), 
       device = "eps",
       units = "mm",
       width = 40,
       height = 50)
```

@@

write_tsv(x = decreased_Rec,
          file = here("results/semi_tryptic/proteolytic_products_decreased_in_Recurrent.tsv"))
